---
title: "Developing-Data-Products-Week4rmd"
author: "GaryFH"
date: "May 26, 2017"
output: html_document
---

```##{r setup, include=FALSE}
##knitr::opts_chunk$set(echo = FALSE)
```

## Find best regressors set up function called "BestFitVar" (an x,y,z function) - note for this to work the data must be in a data.frame format and the dependent variable needs to be the first column.

### x= database,   y= number of best regressors you want to find,  z= if 1 then Adusted R squared is criteria for choosing the best regressors - any other value for z means Pvalue is the criteria method

```{r ,warning=FALSE,message=FALSE}
library(caret);library(dplyr);library(ggplot2)
```

```{r}
BestFitVar<-function(x,y,z) {
         
         
## Remove near zero and mostly NA variables - Near zero only works if all variables are numeric!

                        ## nza<-nearZeroVar(x) - 
                        ## x<-x[,-nza]
        mostNA<-sapply(x, function(x) mean(is.na(x)))>=.95
        x<-x[,mostNA==F]

## Remove dependent variable from potential regressors                
        x1<-x[,-1]
        
## Insure that the number of good regressors wanted does not exceed the number available
        
                NumOfRegressors<-ncol(x1)
            if(NumOfRegressors<y) stop("there are less than (y) regressors")
                pval<-numeric(NumOfRegressors)
                AdjR<-numeric(NumOfRegressors)
## Find best regressors (those with lowest P-values)

            for(i in seq_len(NumOfRegressors)) {
                fit<-lm(x[,1]~x1[,i])
                s<-summary(fit)
                pval[i]<-s$coefficients[2,4]
                AdjR[i]<-s$adj.r.squared
                        #print(names(s))
                        #print(s)
                        #print(class(pval))
                        #print(pval)
                        #regname<-names(x1)
                        #print(regname)
              }
## make new data.frame by removing extra regressors 
        if(z==1){criteria<-AdjR}
        if(!z==1){criteria<-pval} 
                
        LowToHigh <- order(criteria)
        LowToHigh<- LowToHigh[1:y]
        xLowval<-x1[,(LowToHigh)]
        Regressor_lowest<-names(xLowval)
                        #print(LowToHigh)
                        #print(names(xLow))
                        #print(a1)
                
 #prepare and print
                                
        AdjustedRSquared<-round(AdjR[LowToHigh],4)
        Pvalues<-signif(pval[LowToHigh],4)
                a1<-table(Regressor_lowest,AdjustedRSquared,Pvalues)
                a2<-tbl_df(a1)
                a2$Pvalues<-as.numeric(a2$Pvalues)
                a2$AdjustedRSquared<-as.numeric(a2$AdjustedRSquared)
                a3<-filter(a2,n>0)
                a4<-select(a3,-n)
                ##a4<-arrange(a4,Pvalues)
                a5<-as.matrix(a4)
                print(a5,quote = F)
                rownames(a5)<-rep("",nrow(a5))
        ##
}
```

## Example using mtcars database
###Put dependent variable in first column 
```{r}

BestFitVar(mtcars,4,1)  ##Adusted R squared criteria
BestFitVar(mtcars,4,2)  ##Pvalue criteria
```

## Example using diamonds database (part of ggplot2)

###Put dependent variable in first column and remove unwanted variables (x,y,z)

```{r setup}

d1<-tbl_df(diamonds)
d2<-select(d1,price,carat:table) ## price first column
d2<-as.data.frame(d2)

###next put in function x=database,y=numberof best variables you want to find
BestFitVar(d2,4,2) ##Pvalue criteria
BestFitVar(d2,4,1) ##Adusted R squared criteria
```

## Example using airquality database - no prep is required
###Put dependent variable in first column

```{r}
BestFitVar(airquality,4,2) ##Pvalue criteria
BestFitVar(airquality,4,1)##Adusted R squared criteria
```



##``
## Example using state database
###Put dependent variable in first column 

```{r}
state<-as.data.frame(state.x77)
BestFitVar(state,5,2) ##Pvalue criteria
BestFitVar(state,5,1)##Adusted R squared criteria
```



